---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file and then run `devtools::build_readme()` to render with the latest version of the code.-->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OpenStreetMap's tagging datasets

<!-- badges: start -->

[![DOI](https://zenodo.org/badge/1165670803.svg)](https://doi.org/10.5281/zenodo.18833755)

<!-- badges: end -->

The goal of `{osmtaggingr}` is to provide reproducible datasets containing information about [OpenStreetMap](http://openstreetmap.org)'s tagging proposals. It does so by querying and webscrapping OSM's wiki via helper functions. 

The package contains the following:

1. Datasets (`proposals`) and associated metadata (see `?proposals`)
2. Helper functions and description


## Acknowledgements

This is an output of the research project _["Can digital goods be neutral? Evaluating OpenStreetMap’s equity through participatory data visualisation"](https://warwick.ac.uk/fac/cross_fac/cim/research/digital-good-neutrality-osm)_ led by Carlos Cámara-Menoyo and Timothy Monteath and funded by the [ESRC Digital Good Network](https://digitalgood.net/) through their Digital Good Research Fund 2024-25. 


## Citing

You are free to use and reuse this tool under the licence conditions.  
If you use this package in your work, please cite it as below:

> Cámara-Menoyo C, Monteath T (2026). OSMtaggingR: Creates OpenStreetMap's tagging Datasets. R package version 0.0.0.9000, https://github.com/WarwickCIM/OSMtaggingR.

```bibtex
@Manual{,
  title = {OSMtaggingR: Creates OpenStreetMap's tagging Datasets},
  author = {Carlos Cámara-Menoyo and Timothy Monteath},
  year = {2026},
  note = {R package version 0.0.0.9000},
  url = {https://github.com/WarwickCIM/OSMtaggingR},
}
```



## Installation

You can install the development version of osmtaggingr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("warwickcim/osmtaggingr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(osmtaggingr)

# Load the built in datasets.
data(proposals)

# Converting to tibble for better representation.
proposals <- tibble::as_tibble(proposals)

# Explore the dataset.
head(proposals)

colnames(proposals)

# Check the dataset's metadata
?proposals
```

